\addcontentsline{toc}{chapter}{Conference Proceedings}

\begin{center}
	%{{\fontsize{16}{15} \bf ABSTRACT}\\}
	{\fontsize{16}{15} \bf Conference Proceedings \\ \vspace{0.3cm}
		}
	\vspace{0.4cm}
\end{center}
\normalsize
\begin{itemize}
\item[1] Muhammad Umar Javed, \underline{\textbf{Abid Jamal}}, Nadeem Javaid, Noman Haider, and Muhammad Imran. "Conditional Anonymity enabled Blockchain-based Ad Dissemination in Vehicular Ad-hoc Network." In 2020 International Wireless Communications and Mobile Computing (IWCMC), pp. 2149-2153. IEEE, 2020. {\href{https://ieeexplore.ieee.org/abstract/document/9148487}{Download}}

\item[2] Affaf Shahid, Umair Sarfraz, Muhammad Waseem Malik, Muhammad Sohaib Iftikhar, \underline{\textbf{Abid Jamal}} and Nadeem Javaid, "Blockchain-Based Reputation System in Agri-Food Supply Chain", Advanced Information Networking and Applications. AINA 2020. Advances in Intelligent Systems and Computing, vol 1151. Springer, 2020. {\href{https://link.springer.com/chapter/10.1007/978-3-030-44041-1_2}{Download}}

\item[3] Asad Ullah Khan, Affaf Shahid, Fatima Tariq, Abdul Ghaffar, \underline{\textbf{Abid Jamal}}, Shahid Abbas and Nadeem Javaid, "Enhanced Decentralized Management of Patient-Driven Interoperability Based on Blockchain",Advances on Broad-Band Wireless Computing, Communication and Applications. BWCCA 2019. Lecture Notes in Networks and Systems, vol 97. Springer, 2019. {\href{https://link.springer.com/chapter/10.1007/978-3-030-33506-9_74}{Download}}

\item[4] \underline{\textbf{ Abid Jamal}}, Sana Amjad, Usman Aziz, Muhammad Usman Gurmani, Saba Awan and Nadeem Javaid, "A Privacy Preserving Hybrid Blockchain based Announcement Scheme for Vehicular Energy Network", in the 15th International Conference on Complex, Intelligent and Software Intensive System (CISIS), 2021, ISBN: 978-3-030-50454-0.
{\href{https://www.researchgate.net/publication/351133979_A_Privacy_Preserving_Hybrid_Blockchain_based_Announcement_Scheme_for_Vehicular_Energy_Network}{Download}}

\item[5] \underline{\textbf{Abid Jamal}}, Muhammad Usman Gurmani, Saba Awan, Maimoona Bint E Sajid, Sana Amjad and Nadeem Javaid, "Blockchain enabled Secure and Efficient Reputation Management for Vehicular Energy Network", in the 15th International Conference on Complex, Intelligent and Software Intensive System (CISIS), 2021, ISBN: 978-3-030-50454-0.
{\href{https://www.researchgate.net/publication/351133976_Blockchain_enabled_Secure_and_Efficient_Reputation_Management_for_Vehicular_Energy_Network}{Download}}


\end{itemize}
\clearpage
\newpage 