\chapter[]{References}
\label{chp:7}
\begin{singlespace}
\renewcommand{\bibname}{References}
%\bibliography{main}
\begin{thebibliography}{}



    \bibitem{dnn_archi}Liu, W., Wang, Z., Liu, X., Zeng, N., Liu, Y. and Alsaadi, F.E., 2017. A survey of deep neural network architectures and their applications. Neurocomputing, 234, pp.11-26.
    \bibitem{Hassija}Hassija, V., Chamola, V., Mahapatra, A., Singal, A., Goel, D., Huang, K., Scardapane, S., Spinelli, I., Mahmud, M. and Hussain, A., 2024. Interpreting black-box models: a review on explainable artificial intelligence. Cognitive Computation, 16(1), pp.45-74.

     \bibitem{Liang}Liang, Y., Li, S., Yan, C., Li, M. and Jiang, C., 2021. Explaining the black-box model: A survey of local interpretation methods for deep neural networks. Neurocomputing, 419, pp.168-182.
    \bibitem{adv_attacks}Ren, K., Zheng, T., Qin, Z. and Liu, X., 2020. Adversarial attacks and defenses in deep learning. Engineering, 6(3), pp.346-360.

    \bibitem{deeptest}Tian, Y., Pei, K., Jana, S. and Ray, B., 2018, May. Deeptest: Automated testing of deep-neural-network-driven autonomous cars. In Proceedings of the 40th international conference on software engineering (pp. 303-314).
    
    \bibitem{deepxplore} Pei, K., Cao, Y., Yang, J. and Jana, S., 2017, October. Deepxplore: Automated whitebox testing of deep learning systems. In proceedings of the 26th Symposium on Operating Systems Principles (pp. 1-18).

    \bibitem{deepguage}Ma, L., Juefei-Xu, F., Zhang, F., Sun, J., Xue, M., Li, B., Chen, C., Su, T., Li, L., Liu, Y. and Zhao, J., 2018, September. Deepgauge: Multi-granularity testing criteria for deep learning systems. In Proceedings of the 33rd ACM/IEEE international conference on automated software engineering (pp. 120-131).
    
    \bibitem{SunY}Sun, Y., Huang, X., Kroening, D., Sharp, J., Hill, M. and Ashmore, R., 2018. Testing deep neural networks. arXiv preprint arXiv:1803.04792.

    \bibitem{KimJ}Kim, J., Feldt, R. and Yoo, S., 2019, May. Guiding deep learning system testing using surprise adequacy. In 2019 IEEE/ACM 41st International Conference on Software Engineering (ICSE) (pp. 1039-1049). IEEE.
  
   
    \bibitem{dlfuzz}Guo, J., Jiang, Y., Zhao, Y., Chen, Q. and Sun, J., 2018, October. Dlfuzz: Differential fuzzing testing of deep learning systems. In Proceedings of the 2018 26th ACM Joint Meeting on European Software Engineering Conference and Symposium on the Foundations of Software Engineering (pp. 739-743).

    \bibitem{tensorfuzz} Odena, A., Olsson, C., Andersen, D. and Goodfellow, I., 2019, May. Tensorfuzz: Debugging neural networks with coverage-guided fuzzing. In International Conference on Machine Learning (pp. 4901-4911). PMLR.

    \bibitem{deepconcolic}Sun, Y., Huang, X., Kroening, D., Sharp, J., Hill, M. and Ashmore, R., 2019, May. DeepConcolic: Testing and debugging deep neural networks. In 2019 IEEE/ACM 41st International Conference on Software Engineering: Companion Proceedings (ICSE-Companion) (pp. 111-114). IEEE.

    \bibitem{Intro_1} Sekhon, Jasmine, and Cody Fleming. "Towards improved testing for deep learning." 2019 IEEE/ACM 41st International Conference on Software Engineering: New Ideas and Emerging Results (ICSE-NIER). IEEE, 2019.

\bibitem{Agarwal} Agarwal, Aniya, et al. "Automated test generation to detect individual discrimination in AI models." arXiv preprint arXiv:1809.03260 (2018).

\bibitem{Youcheng} Sun, Youcheng, et al. "Concolic testing for deep neural networks." Proceedings of the 33rd ACM/IEEE International Conference on Automated Software Engineering. 2018.

\bibitem{Kexin} Pei, Kexin, et al. "DeepXplore." Communications of the ACM 62.11 (2019): 137-145.

\bibitem{Yuchi} Tian, Yuchi, et al. "Deeptest: Automated testing of deep-neural-network-driven autonomous cars." Proceedings of the 40th international conference on software engineering. 2018.

\bibitem{Sun} Sun, Youcheng, et al. "Testing deep neural networks." arXiv preprint arXiv:1803.04792 (2018).

\bibitem{Ma} Ma, Lei, et al. "Deepgauge: Multi-granularity testing criteria for deep learning systems." Proceedings of the 33rd ACM/IEEE international conference on automated software engineering. 2018.

\bibitem{Zhang} Zhang, Mengshi, et al. "DeepRoad: GAN-based metamorphic testing and input validation framework for autonomous driving systems." Proceedings of the 33rd ACM/IEEE International Conference on Automated Software Engineering. 2018.

\bibitem{Xie} Xie, Xiaofei, et al. "Deephunter: Hunting deep neural network defects via coverage-guided fuzzing." arXiv preprint arXiv:1809.01266 (2018).

\bibitem{Gopinath}	Gopinath, Divya, et al. "Symbolic execution for deep neural networks." arXiv preprint arXiv:1807.10439 (2018).

\bibitem{DeRaedt}
De Raedt, L., Kimmig, A. and Toivonen, H., 2007, January. Problog: A probabilistic prolog and its application in link discovery. In IJCAI (Vol. 7, pp. 2462-2467).

\bibitem{DeepProbLog}
Manhaeve, R., Dumancic, S., Kimmig, A., Demeester, T. and De Raedt, L., 2018. Deepproblog: Neural probabilistic logic programming. Advances in neural information processing systems, 31.
 
\end{thebibliography}
\bibliographystyle{plain}
\end{singlespace}
